Testing Set Features Visualization

### 2022-10-28 TestingPipeline/Scripts/combining_tool_output.Rmd
Updating rules with different viral types from VS2.

get rid of NAs for downstream processing
```{r}
# checkV
viruses$percent_viral[is.na(viruses$percent_viral)] <- 0
viruses$percent_unknown[is.na(viruses$percent_unknown)] <- 0
viruses$checkv_completeness[is.na(viruses$checkv_completeness)] <- 0
# VIBRANT
viruses$vibrant_quality[is.na(viruses$vibrant_quality)] <- 0
# DeepVirFinder
viruses$score[is.na(viruses$score)] <- 0
viruses$bh_pvalue[is.na(viruses$bh_pvalue)] <- 0
# VirSorter2
viruses$viral[is.na(viruses$viral)] <- 0
viruses$hallmark[is.na(viruses$hallmark)] <- 0
#Virsorter
viruses$category[is.na(viruses$category)] <- 0
# Kaiju
viruses$Kaiju_Viral[is.na(viruses$Kaiju_Viral)] <- "unknown"
viruses$Kingdom[is.na(viruses$Kingdom)] <- "unknown"
```

>>>>

get rid of NAs for downstream processing
```{r}
# checkV
viruses$percent_viral[is.na(viruses$percent_viral)] <- 0
viruses$percent_unknown[is.na(viruses$percent_unknown)] <- 0
viruses$checkv_completeness[is.na(viruses$checkv_completeness)] <- 0
# VIBRANT
viruses$vibrant_quality[is.na(viruses$vibrant_quality)] <- 0
# DeepVirFinder
viruses$score[is.na(viruses$score)] <- 0
viruses$bh_pvalue[is.na(viruses$bh_pvalue)] <- 0
# VirSorter2
viruses$viral[is.na(viruses$viral)] <- 0
viruses$hallmark[is.na(viruses$hallmark)] <- 0
viruses$RNA[is.na(viruses$RNA)] <- 0
viruses$lavidaviridae[is.na(viruses$lavidaviridae)] <- 0
viruses$NCLDV[is.na(viruses$NCLDV)] <- 0
viruses$ssDNA[is.na(viruses$ssDNA)] <- 0
viruses$dsDNAphage[is.na(viruses$dsDNAphage)] <- 0

#Virsorter
viruses$category[is.na(viruses$category)] <- 0
# Kaiju
viruses$Kaiju_Viral[is.na(viruses$Kaiju_Viral)] <- "unknown"
viruses$Kingdom[is.na(viruses$Kingdom)] <- "unknown"
```

### 2022-10-28 TestingPipeline/Scripts/rule_tuning_2022.09.06.Rmd
Updating rules with different viral types from VS2.

```{r}
viruses$checkv_completeness[is.na(viruses$checkv_completeness)] <- 0
```

@@

  if (include_virsorter2) {
    keep_score[input_seqs$viral>=50] <- keep_score[input_seqs$viral>=50] + 0.5
    keep_score[input_seqs$viral>=95] <- keep_score[input_seqs$viral>=95] + 0.5
  }

@@

## high MCC example
```{r}
viruses$keep_score_high_MCC <- getting_viral_set_1(viruses, include_deepvirfinder = F,
                                              include_vibrant = T,
                                              include_virsorter2 = T,
                                              include_kaiju = T,
                                              include_tuning = T,
                                              include_virsorter = T)
```

>>>>

@@

  if (include_virsorter2) {
    keep_score[input_seqs$viral>=50] <- keep_score[input_seqs$viral>=50] + 0.5
    keep_score[input_seqs$viral>=95] <- keep_score[input_seqs$viral>=95] + 0.5
    keep_score[input_seqs$RNA>=0.9] <- keep_score[input_seqs$RNA>=0.9] + 0.5
    keep_score[input_seqs$lavidaviridae>=0.9] <- keep_score[input_seqs$lavidaviridae>=0.9] + 0.5
    keep_score[input_seqs$NCLDV>=0.9] <- keep_score[input_seqs$NCLDV>=0.9] + 0.5
  }

@@

## high MCC example
```{r}
viruses$keep_score_high_MCC <- getting_viral_set_1(viruses, include_deepvirfinder = F,
                                              include_vibrant = T,
                                              include_virsorter2 = T,
                                              include_tuning_viral = T,
                                              include_tuning_not_viral = T,
                                              include_virsorter = T)
```

### 2022-10-28 TestingPipeline/Scripts/testing_set_features_visualization.Rmd
Adjusting rules to help with false positive protists.
Updating rules with different viral types from VS2.

@@

>>>>

```{r}
plot(viruses$RNA, viruses$viral)
plot(viruses$lavidaviridae, viruses$viral)
plot(viruses$NCLDV, viruses$viral)
plot(viruses$ssDNA, viruses$viral)
```

@@

```{r}
ggplot(viruses, aes(x=hallmark, y=checkv_completeness)) +
  geom_hex(bins = 30) +
  scale_fill_continuous(type = "viridis", trans="log10") +
  theme_bw() +
  facet_wrap(~seqtype, scales = "free") +
  xlab("Hallmark Genes") +
  ylab("Completeness") 
```
